Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
edits

5) In relation to all the previous questions: how do individuals vary in their assessment of the costs and benefits of swimming between islands? Why did some caribou regularly engage in swimming events, while more than half of our marked population were never observed swimming in the ocean? The forage limitation hypothesis is generally thought to apply uniformly across populations, but individual caribou could evaluate the costs and benefits of swimming to another island differently. It is possible that some individuals, in our case ~10%, considered swimming to be less costly or perceived competition or predation more acutely than their conspecifics.

@@

Oceanic swimming is relatively common among a minority of marked caribou. Of the
three collared individuals that swam the most, two were collared on Western
Indian Island and the third was collared on Fogo Island. Inter-island distances
between Western and Eastern Indian Islands, and the smaller islands around them,
are shorter than those between Fogo Island and others (Figure 2). It is possible
that caribou display natal philopatry [e.g. @Larue2018] to some of the smaller
islands and thus are more likely to swim between them more frequently than
animals that were born, or spend most of their time, on Fogo Island. The forage
limitation hypothesis is generally thought to apply uniformly across
populations, but individual caribou could evaluate the costs and benefits of
swimming to another island differently. It is possible that some individuals, in
our case ~10%, considered swimming to be less costly or perceived competition or
predation more acutely than their conspecifics.

>>>>

5) In relation to all the previous questions: how do individuals vary in their
assessment of the costs and benefits of swimming between islands? Why did some
caribou regularly engage in swimming events, while more than half of our marked
population were never observed swimming in the ocean? The forage limitation
hypothesis is thought to apply uniformly across populations, but
individual caribou could evaluate the costs and benefits of swimming to another
island differently. It is possible that some individuals, in our case ~10%,
considered swimming to be less costly or perceived competition or predation more
acutely than their conspecifics.

Oceanic swimming is relatively common among a minority of marked caribou. Of the
three collared individuals that swam the most, two were collared on Western
Indian Island and the third was collared on Fogo Island. Inter-island distances
between Western and Eastern Indian Islands, and the smaller islands around them,
are shorter than those between Fogo Island and others (Figure 2). It is possible
that caribou display natal philopatry [e.g. @Larue2018] to some of the smaller
islands and thus are more likely to swim between them more frequently than
animals that were born, or spend most of their time, on Fogo Island.

@@
